msre core

### 2019-05-24 report/msrecore.tex
intermediate update, with lots and lots of changes.

\documentclass{article}
\usepackage[active,tightpage]{preview}
\renewcommand{\PreviewBorder}{1in}
\usepackage{float}

@@

\usepackage{graphicx}
\usepackage[figurename=figure,tablename=table]{caption}
\usepackage[autostyle]{csquotes}
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{msrecore.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black
}
\urlstyle{same}

@@

\begin{document}
\begin{preview}
\maketitle

\section{introduction}
the design and dimensions of the molten salt reactor experiment is detailed in several ornl reports. this document aims at providing a comprehensive overview of the core design, dimensions, and materials, for the purpose of creating an accurate cad model of the reactor core.
care is taken to give proper references to the original data, figure, tables, etc. likewize, any quantity or feature laking documentation og reference not yet found will be extrapolated from the available information.

\section{msre core}
isometric view of the msre core can be seen in figure \ref{3229-fig1}
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=5,width=0.8\textwidth,trim={2cm 6cm 3.5cm 4cm},clip]{./references/ORNL-TM-3229.pdf}}
  \caption{msre reactor vessel \parencite[figure 1]{ornl-tm-3229}.}
  \label{3229-fig1}
\end{figure}
% \begin{figure}[H]
%   \centering
%   \fbox{\includegraphics[page=9,width=0.8\textwidth,trim={4cm 4cm 2.5cm 3cm},clip]{./references/ORNL-TM-0378.pdf}}
%   \caption{isometric view of the msre reactor vessel (older design) \parencite[figure 1]{ornl-tm-0378}.}
%   \label{0378-fig1}
% \end{figure}
% note that they differ slight, e.g. the vessel drain line and around the control assembly. the latter picture is showing an ealier design, this serves as a precautious warning when determing the msre design from ornl reports.
% the two drain lines seen in figure \ref{3229-fig1} and \ref{0378-fig1} are described in section \ref{sec:drain}.

@@

table \ref{61246-tab4} gives many of the key dimensions of the core \ref{3229-fig1}.
\begin{table}[H]
  \centering
  \fbox{\includegraphics[page=11,width=0.8\textwidth,trim={2cm 3.5cm 2cm 3.5cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \caption{reactor vessel design data \parencite[table 4]{ad-cf-61-2-46}.}
  \label{61246-tab4}
\end{table}

figure \ref{4233-fig2} gives the relative possitions of the core vessel, graphite core, and control assembly.
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=16,width=0.8\textwidth,trim={2cm 5cm 3cm 3cm},clip]{./references/ORNL-4233.pdf}}
  \caption{relation of rod position and levels in reactor vessel. \parencite[table 4]{ornl-4233}.}
  \label{4233-fig2}
\end{figure}

figure \ref{0728-p109-p110} shows a section view of the msre core
\begin{figure}[H]
  \centering
  \fbox{
  \begin{tabular}{c}
    \includegraphics[page=109,width=0.8075\textwidth,trim={2.5cm 0.04cm 2.5cm 17cm},clip]{./references/ORNL-TM-0728.pdf}\\[-0.12cm]
    \includegraphics[page=110,width=0.8\textwidth,trim={2.64cm 27cm 2.5cm 0.04cm},clip]{./references/ORNL-TM-0728.pdf}
  \end{tabular}
  }
  \caption{cross section of msre reactor vessel and access nozzle \parencite[page 109-110]{ornl-tm-0728}.}
  \label{0728-p109-p110}
\end{figure}

the arangement of the graphite stringers are detailed in figure \ref{4174-p10-p11}
\begin{figure}[H]
  \centering
  \fbox{
  \includegraphics[page=10,width=0.42\textwidth,trim={1cm 3cm 0.25cm 4cm},clip]{./references/ORNL-TM-4174.pdf}
  \hspace{-0.2cm}
  \includegraphics[page=11,width=0.36\textwidth,trim={2cm 3.1cm 3cm 4cm},clip]{./references/ORNL-TM-4174.pdf}
  }
  \caption{reactor core block assembly plan, drawing D-BB-B-40416 \parencite[page 10-11]{ornl-tm-4174}.}
  \label{4174-p10-p11}
\end{figure}

@@

\textcolor{cyan}{the shape of the reactor vessel is still unknown, but the asme standards should allow for approximate dimensioning, for now it's done by tracing figure \ref{0728-p109-p110}.}

\subsection{flow distributor and annulus}
\textcite[page 112 and 114]{ornl-tm-3039} states about the annulus: \enquote{\textit{the fuel salt entered the flow distributor where it was directed downward around the circumference of the vessel. it flowed in a spiral path through a 1-in. annulus between the vessel wall and the core can for cooling purposes.}}. \enquote{\textit{to prevent possible overheating in an otherwise stagnant region, a small portion of salt entering the reactor was diverted into the region just above the core can support flange in the annulus between the vessel and the core can}}.
this is depicted in figure \ref{0728-p109-p110}.

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=5,width=0.8\textwidth,trim={6.3cm 11.3cm 4.8cm 14.5cm},clip]{./references/ORNL-TM-3229.pdf}}
  \caption{zoomed in view of the flow distributor orifices from figure \ref{3229-fig1} \parencite[figure 1]{ornl-tm-3229}.}
  \label{3229-fig1-zoom}
\end{figure}

\textcolor{cyan}{still unknown are the vertical position and spacing of the stacked three holes, the point at which they start, and how the spacing around the flow distributor increases.}

\subsubsection{bypass flow}
\parencite[page 85]{ornl-tm-0728} states about the bipass:
\enquote{\textit{to prevent possible overheating in a region that might otherwise have been stagnant, about 24 gpm of salt entering the reactor is diverted into the region just above the core-can support flange in the annulus between the pressure vessel and the core can. this is accomplished through 18 slots or channels, 0.2 by 0.2 in., cut in the core-can flange. these slots are machined at an angle of $30^\circ$ to promote better mixing in the region. in addition, a by-pass flow of 3-22 gpm of salt will pass through the annular clearances at the core can support ring}}.

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=84,width=0.8\textwidth,trim={4cm 3.9cm 4.7cm 14.5cm},clip,angle=0.3]{./references/ORNL-3708.pdf}}
  \caption{reactor vessel ready to accept graphite core assembly \parencite[figure 39]{ornl-3708}.}
  \label{3708-fig39}
\end{figure}

\subsection{anti-swirl vanes}
\textcite[page 14]{ornl-tm-3229} states about the anti-swirl vanes: \enquote{\textit{the anti-swirl vanes consist of 48 plates starting about 2 in. up in the core wall cooling annulus and extending along radial lines into the lower head for about 38\% of the radial distance to the core centerline. they are slightly elevated of the core vessel wall, thus eliminating as much coner area as possible where settled solids could accumulate.}}.

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=19,width=0.8\textwidth,trim={2cm 7.5cm 3.5cm 4.5cm},clip]{./references/ORNL-TM-3229.pdf}}
  \caption{anti-swirl vanes and radial pressure gradient at walls of lower vessel head \parencite[figure 9]{ornl-tm-3229}.}
  \label{3229-fig9}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=5,width=0.8\textwidth,trim={7cm 7cm 13cm 20.5cm},clip]{./references/ORNL-TM-3229.pdf}}
  \caption{zoomed in view of the anti-swirl vanes from figure \ref{3229-fig1} \parencite[figure 1]{ornl-tm-3229}.}
  \label{3229-fig1-zoom-strainer}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
  \includegraphics[page=83,width=0.4\textwidth,trim={4.8cm 4.2cm 4cm 14.2cm},clip,angle=-0.1]{./references/ORNL-3708.pdf}
  \includegraphics[page=25,width=0.439\textwidth,trim={4cm 14.4cm 2.6cm 3.3cm},clip]{./references/ORNL-3369.pdf}
  }
  \caption{attachment of flow-straightening vanes to reactor vessel \parencite[figure 37]{ornl-3708} (right) inside of reactor vessel showing flow straightening vanes \parencite[figure 1.3]{ornl-3369} (left).}
  \label{3369-fig1.3}
\end{figure}

\textcolor{cyan}{still unknown are the curves on the lower side of the anti-swirl vanes, seen in figure \ref{3229-fig1-zoom-strainer} and the thichness of the anti-swirl vanes.}

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=110,width=0.8\textwidth,trim={7.5cm 27.5cm 8.2cm 12cm},clip]{./references/ORNL-TM-0728.pdf}}
  \caption{zoomed in view of drain from figure \ref{0728-p109-p110} \parencite[page 110]{ornl-tm-0728}.}
\end{figure}

\textcolor{cyan}{still unknown is length of both pipes protrusion into the vessel and the angle and size of the umbrella and how it attaches to the drain pipe. furthermore, the pipes and umbrella wall thickness is unknown.}

@@

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=110,width=0.8\textwidth,trim={7.5cm 30.5cm 8.2cm 9.9cm},clip]{./references/ORNL-TM-0728.pdf}}
  \caption{zoomed in view of the grid support plates from figure \ref{0728-p109-p110} \parencite[page 110]{ornl-tm-0728}.}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=5,width=0.6\textwidth,trim={9cm 8cm 10.5cm 18.5cm},clip]{./references/ORNL-TM-3229.pdf}}
  \caption{zoomed in view of the grid support plates from figure \ref{3229-fig1} \parencite[figure 1]{ornl-tm-3229}.}
\end{figure}

\textcolor{cyan}{still unknown many of the key dimensions and positions. we e.g. see holes for the hold-down rods in the zoomed image above which is not even mentioned.}

\subsection{vessel outlet}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=25,width=0.8\textwidth,trim={2.5cm 2cm 2cm 1.5cm},clip]{./references/AD-CF-61-2-46.pdf}}
  \caption{msre control system \parencite[figure 14c]{ad-cf-61-2-46}.}
  \label{61246-fig14c}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=122,width=0.8\textwidth,trim={4cm 4.5cm 4cm 3cm},clip]{./references/ORNL-TM-3039.pdf}}
  \caption{reactor access nozzle showing 10- and 2-1/2 in. annuli  \parencite[figure 5.10]{ornl-tm-3229}.}
  \label{3039-fig5-10}
\end{figure}

\subsubsection{outlet strainer}
\textcite[page 24-26]{ornl-tm-3229} states about the outlet strainer: \enquote{\textit{after the model was built, a strainer structure ... was added to the reactor outlet design which penetrated down into the upper plenum. its purpose was to catch graphite chips (graphite floats in fuel salt) should they break loose from the moderator. this device was not installed in the model but it would not be expected to incluence the flow significantly}}.

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=123,width=0.8\textwidth,trim={4cm 8cm 2.5cm 3.5cm},clip]{./references/ORNL-TM-3039.pdf}}
  \caption{reactor fuel outlet strainer \parencite[figure 5.11]{ornl-tm-3229}.}
  \label{3039-fig5-11}
\end{figure}

\textcite[page 115]{ornl-tm-3039} states about the outlet strainer: \enquote{\textit{stainers were provided at the reactor outlet to prevent passage of graphite chips larger then 1/16 in. a strainer basket was attached to the lower end of the 10-in. nozzle plug and extended downward into the upper head region of the reactor vessel. the three control rod timbles and the graphite sample assembly passed through the stainer basket. since the five graphite elements were not pinned as were the remaining moderator elements, a cross-shaped extension of the basket essembly projected beneath the basket to provide a hold-down}}. this is depicted in figure \ref{3039-fig5-11}.

@@

\textcolor{cyan}{still unknown are a lot of details on outlet, plug, and strainer.}

>>>>

\documentclass{article}
\usepackage{geometry}
\geometry{paperwidth=170mm,
          paperheight=2500mm,
          top=20mm,
          bottom=20mm
          }
\usepackage{float}

@@

\usepackage{graphicx}
\usepackage[figurename=figure,tablename=table,width=.75\textwidth]{caption}
\usepackage[autostyle]{csquotes}
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{msrecore.bib}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black
}
\urlstyle{same}
\usepackage{pgf}

\newcommand*{\mrsarchive}{../../msr-archive}%

@@

\begin{document}
\maketitle

\section{introduction}
the design and dimensions of the molten salt reactor experiment is detailed in several ornl reports. this document aims at providing a comprehensive overview of the core design, dimensions, and materials, for the purpose of creating an accurate cad model of the reactor core. \\

care is taken to give proper references to the original data, figure, tables, etc. likewise, any quantity or feature laking documentation or reference not yet found will be estimated or extrapolated from the available information.

\section{msre core}
an isometric view of the msre core can be seen in figure \ref{3229-fig1}
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=6,width=0.8\textwidth,trim={2cm 6cm 3.5cm 4cm},clip]{\mrsarchive/docs/ORNL-TM-3229.pdf}}
  \caption{msre reactor vessel \parencite[figure 1]{ornl-tm-3229}.}
  \label{3229-fig1}
\end{figure}

@@

table \ref{61246-tab4} gives many of the key dimensions of the core \ref{3229-fig1}.
\begin{table}[H]
  \centering
  \fbox{\includegraphics[page=11,width=0.8\textwidth,trim={2cm 3.5cm 2cm 3.5cm},clip]{\mrsarchive/docs/ORNL-CF-61-2-46-AD.pdf}}
  \caption{reactor vessel design data \parencite[table 4]{ad-cf-61-2-46}.}
  \label{61246-tab4}
\end{table}

figure \ref{4233-fig2} gives the relative possitions of the core vessel, graphite core, and control assembly.
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=16,width=0.8\textwidth,trim={2cm 5cm 3cm 3cm},clip]{\mrsarchive/docs/ORNL-4233.pdf}}
  \caption{relation of rod position and levels in reactor vessel. \parencite[table 4]{ornl-4233}.}
  \label{4233-fig2}
\end{figure}

figure \ref{0728-p109-p110} shows a section view of the msre core
\begin{figure}[H]
  \centering
  \fbox{
  \begin{tabular}{c}
    \includegraphics[page=109,width=0.8075\textwidth,trim={2.5cm 0.04cm 2.5cm 17cm},clip]{\mrsarchive/docs/ORNL-TM-0728.pdf}\\[-0.12cm]
    \includegraphics[page=110,width=0.8\textwidth,trim={2.64cm 27cm 2.5cm 0.04cm},clip]{\mrsarchive/docs/ORNL-TM-0728.pdf}
  \end{tabular}
  }
  \caption{cross section of msre reactor vessel and access nozzle \parencite[page 109-110]{ornl-tm-0728}.}
  \label{0728-p109-p110}
\end{figure}

the arangement of the graphite stringers are detailed in figure \ref{4174-p10-p11}
\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=13,width=0.8\textwidth,trim={5.5cm 2cm 1.5cm 2.5cm},clip,angle=-0.25]{\mrsarchive/docs/ORNL-TM-4174.pdf}}
  \caption{reactor core block assembly plan, drawing D-BB-B-40416 \parencite[page 13]{ornl-tm-4174}.}
  \label{4174-p10-p11}
\end{figure}

@@

\subsection{flow distributor and annulus}
\textcite[page 112 and 114]{ornl-tm-3039} states about the annulus:
\enquote{\textit{the fuel salt entered the flow distributor where it was directed downward around the circumference of the vessel. it flowed in a spiral path through a 1-in. annulus between the vessel wall and the core can for cooling purposes.}}. \enquote{\textit{to prevent possible overheating in an otherwise stagnant region, a small portion of salt entering the reactor was diverted into the region just above the core can support flange in the annulus between the vessel and the core can}}.
this is depicted in figure \ref{0728-p109-p110}. \\

\parencite[page 108]{ornl-tm-0728} states about the flow distributor and inlet:
\enquote{\textit{salt is delivered to the holes through a flow distributor, half-circular in cross section, and with an inside radius of about 4 in. the 6-in.-diam inlet to the distributor is arranged tangentially to the vessel, and the holes enter the vessel at an angle of $30^\circ$ with a tangent to the outer surface to impart a spiraling flow to the salt as it moves downward through the reactor-vessel-wall cooling annulus.}}

note that this is in oppositon to the inlet diameter given in table \ref{61246-tab4}.

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=6,width=0.8\textwidth,trim={6.3cm 11.3cm 4.8cm 14.5cm},clip]{\mrsarchive/docs/ORNL-TM-3229.pdf}}
  \caption{zoomed in view of the flow distributor orifices from figure \ref{3229-fig1} \parencite[figure 1]{ornl-tm-3229}.}
  \label{3229-fig1-zoom}
\end{figure}

\parencite[page 108]{ornl-tm-0728} states about the flow distributor orifices:
\enquote{\textit{the wall thickness of the cylindrical portion is 9/16 .in., except for the top 16 in.; which is 1 in. thick. the extra thickness is needed in the upper section to allow for 84 holes, 3/4 in. in diameter, located with variable spacing around the top of the vessel to distribute the incoming salt evenly around the circumference}}. \\

from this information we can approximate the angular distribution of the orifices. assuming a quadratic relation in the angular position of the stacks of three, of which there are $84/3=28$, and the data set [[1,0],[2,5],[28,337.5]] the resulting fit is $\theta=-4.42308 + 4.13462 n + 0.288462 n^2$, where $n$ is the stack number. tabulating these function results in the following angular positions
\begin{figure}[H]
  \centering
  \begin{tabular}{c|c}
    stack number & angle [${}^\circ$] \\
    \hline
    1 & \pgfmathparse{-4.42308 + 4.13462 * 1 + 0.288462 * 1^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    2 & \pgfmathparse{-4.42308 + 4.13462 * 2 + 0.288462 * 2^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    3 & \pgfmathparse{-4.42308 + 4.13462 * 3 + 0.288462 * 3^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    4 & \pgfmathparse{-4.42308 + 4.13462 * 4 + 0.288462 * 4^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    5 & \pgfmathparse{-4.42308 + 4.13462 * 5 + 0.288462 * 5^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    6 & \pgfmathparse{-4.42308 + 4.13462 * 6 + 0.288462 * 6^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    7 & \pgfmathparse{-4.42308 + 4.13462 * 7 + 0.288462 * 7^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    8 & \pgfmathparse{-4.42308 + 4.13462 * 8 + 0.288462 * 8^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    9 & \pgfmathparse{-4.42308 + 4.13462 * 9 + 0.288462 * 9^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    10 & \pgfmathparse{-4.42308 + 4.13462 * 10 + 0.288462 * 10^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    11 & \pgfmathparse{-4.42308 + 4.13462 * 11 + 0.288462 * 11^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    12 & \pgfmathparse{-4.42308 + 4.13462 * 12 + 0.288462 * 12^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    13 & \pgfmathparse{-4.42308 + 4.13462 * 13 + 0.288462 * 13^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    14 & \pgfmathparse{-4.42308 + 4.13462 * 14 + 0.288462 * 14^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    15 & \pgfmathparse{-4.42308 + 4.13462 * 15 + 0.288462 * 15^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    16 & \pgfmathparse{-4.42308 + 4.13462 * 16 + 0.288462 * 16^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    17 & \pgfmathparse{-4.42308 + 4.13462 * 17 + 0.288462 * 17^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    18 & \pgfmathparse{-4.42308 + 4.13462 * 18 + 0.288462 * 18^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    19 & \pgfmathparse{-4.42308 + 4.13462 * 19 + 0.288462 * 19^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    20 & \pgfmathparse{-4.42308 + 4.13462 * 20 + 0.288462 * 20^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    21 & \pgfmathparse{-4.42308 + 4.13462 * 21 + 0.288462 * 21^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    22 & \pgfmathparse{-4.42308 + 4.13462 * 22 + 0.288462 * 22^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    23 & \pgfmathparse{-4.42308 + 4.13462 * 23 + 0.288462 * 23^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    24 & \pgfmathparse{-4.42308 + 4.13462 * 24 + 0.288462 * 24^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    25 & \pgfmathparse{-4.42308 + 4.13462 * 25 + 0.288462 * 25^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    26 & \pgfmathparse{-4.42308 + 4.13462 * 26 + 0.288462 * 26^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    27 & \pgfmathparse{-4.42308 + 4.13462 * 27 + 0.288462 * 27^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    28 & \pgfmathparse{-4.42308 + 4.13462 * 28 + 0.288462 * 28^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
    29/1 & \pgfmathparse{-4.42308 + 4.13462 * 29 + 0.288462 * 29^2}\pgfmathprintnumberto[precision=1]{\pgfmathresult}{\value}\value \\
  \end{tabular}
\end{figure}

\subsubsection{bypass flow, core support lugs and flange}
\parencite[page 85]{ornl-tm-0728} states about the bypass:
\enquote{\textit{to prevent possible overheating in a region that might otherwise have been stagnant, about 24 gpm of salt entering the reactor is diverted into the region just above the core-can support flange in the annulus between the pressure vessel and the core can. this is accomplished through 18 slots or channels, 0.2 by 0.2 in., cut in the core-can flange. these slots are machined at an angle of $30^\circ$ to promote better mixing in the region. in addition, a by-pass flow of 3-22 gpm of salt will pass through the annular clearances at the core can support ring}}.

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=83,width=0.8\textwidth,trim={4cm 15cm 4.7cm 3cm},clip,angle=0.3]{\mrsarchive/docs/ORNL-3708.pdf}}
  \caption{reactor flow inlet nozzle and flow distributor \parencite[figure 38]{ornl-3708}.}
  % \label{3708-fig38}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=83,width=0.8\textwidth,trim={4cm 3.9cm 4.7cm 14.5cm},clip,angle=0.3]{\mrsarchive/docs/ORNL-3708.pdf}}
  \caption{reactor vessel ready to accept graphite core assembly \parencite[figure 39]{ornl-3708}.}
  \label{3708-fig39}
\end{figure}

\parencite[page 79]{ornl-tm-0728} states about the core support lugs and flange:
\enquote{\textit{the can is supported, and also held down when salt is in the reactor, by a ring at the top of the can which is bolted to 36 lugs welded to the inside wall of the reactor vessel. the can, in turn, supports the graphite used as a moderator material in the reactor.}}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=30,width=0.8\textwidth,trim={4cm 8.75cm 5cm 8.25cm},clip,angle=0.3]{\mrsarchive/docs/ORNL-3626.pdf}}
  \caption{ \parencite[figure 39]{ornl-3626}.}
  \label{3626-fig1-3}
\end{figure}

\subsection{anti-swirl vanes}
\textcite[page 14]{ornl-tm-3229} states about the anti-swirl vanes:
\enquote{\textit{the anti-swirl vanes consist of 48 plates starting about 2 in. up in the core wall cooling annulus and extending along radial lines into the lower head for about 38\% of the radial distance to the core centerline. they are slightly elevated of the core vessel wall, thus eliminating as much coner area as possible where settled solids could accumulate.}}. \\

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=20,width=0.8\textwidth,trim={2cm 7.5cm 3.5cm 4.5cm},clip]{\mrsarchive/docs/ORNL-TM-3229.pdf}}
  \caption{anti-swirl vanes and radial pressure gradient at walls of lower vessel head \parencite[figure 9]{ornl-tm-3229}.}
  \label{3229-fig9}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=6,width=0.8\textwidth,trim={7cm 7cm 13cm 20.5cm},clip]{\mrsarchive/docs/ORNL-TM-3229.pdf}}
  \caption{zoomed in view of the anti-swirl vanes from figure \ref{3229-fig1} \parencite[figure 1]{ornl-tm-3229}.}
  \label{3229-fig1-zoom-strainer}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{
  \includegraphics[page=82,width=0.4\textwidth,trim={4.8cm 4.2cm 4cm 14.2cm},clip,angle=-0.1]{\mrsarchive/docs/ORNL-3708.pdf}
  \includegraphics[page=25,width=0.439\textwidth,trim={4cm 14.4cm 2.6cm 3.3cm},clip]{\mrsarchive/docs/ORNL-3369.pdf}
  }
  \caption{attachment of flow-straightening vanes to reactor vessel \parencite[figure 37]{ornl-3708} (right) inside of reactor vessel showing flow straightening vanes \parencite[figure 1.3]{ornl-3369} (left).}
  \label{3369-fig1.3}
\end{figure}

% \textcolor{cyan}{still unknown are the curves on the lower side of the anti-swirl vanes, seen in figure \ref{3229-fig1-zoom-strainer} and the thichness of the anti-swirl vanes.}

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=110,width=0.8\textwidth,trim={7.5cm 27.5cm 8.2cm 12cm},clip]{\mrsarchive/docs/ORNL-TM-0728.pdf}}
  \caption{zoomed in view of drain from figure \ref{0728-p109-p110} \parencite[page 110]{ornl-tm-0728}.}
\end{figure}

%% \textcolor{cyan}{still unknown is length of both pipes protrusion into the vessel and the angle and size of the umbrella and how it attaches to the drain pipe. furthermore, the pipes and umbrella wall thickness is unknown.}

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=6,width=0.6\textwidth,trim={9cm 8cm 10.5cm 18.5cm},clip]{\mrsarchive/docs/ORNL-TM-3229.pdf}}
  \caption{zoomed in view of the grid support plates from figure \ref{3229-fig1} \parencite[figure 1]{ornl-tm-3229}.}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=110,width=0.8\textwidth,trim={7.5cm 30.5cm 8.2cm 9.9cm},clip]{\mrsarchive/docs/ORNL-TM-0728.pdf}}
  \caption{zoomed in view of the grid support plates from figure \ref{0728-p109-p110} \parencite[page 110]{ornl-tm-0728}.}
\end{figure}

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=165,width=0.8\textwidth,trim={4cm 5.5cm 4cm 2.25cm},clip]{\mrsarchive/docs/ORNL-4676.pdf}}
  \caption{comparison of the bottom positioning stud on the graphite moderator element when initially installed in the msre and after operation \parencite[figure 13.3]{ornl-4676}.}
  \label{4676-fig13-3}
\end{figure}

%% \textcolor{cyan}{still unknown many of the key dimensions and positions. we e.g. see holes for the hold-down rods in the zoomed image above which is not even mentioned.}

\subsection{vessel outlet}
\parencite[page 84-85]{ornl-tm-0728} states about the vessel outlet:
\enquote{\textit{the salt leaves the reactor core and flows through the upper head to the 10-in. nozzle opening. it is diverted through a 5-in. opening in the side of the nozzle to flow to the fuel circulating pump. the 10-in. nozzle also serves as an access port and support for the tree control rods and for taking and placing of the four graphite-sample rods in the core matrix}}.

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=25,width=0.8\textwidth,trim={2.5cm 2cm 2cm 1.5cm},clip]{\mrsarchive/docs/ORNL-CF-61-2-46-AD.pdf}}
  \caption{msre control system \parencite[figure 14c]{ad-cf-61-2-46}.}
  \label{61246-fig14c}
\end{figure}

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=26,width=0.8\textwidth,trim={3.4cm 5.2cm 2cm 4cm},clip]{\mrsarchive/docs/ORNL-4676.pdf}}
  \caption{view of outlet plug \parencite[figure 1.2]{ornl-4676}.}
  \label{4676-fig1-2}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=86,width=0.8\textwidth,trim={6.5cm 4.5cm 5cm 3.25cm},clip]{\mrsarchive/docs/ORNL-3708.pdf}}
  \caption{complete control rod thimble assembly \parencite[figure 43]{ornl-3708}.}
  % \label{3708-fig40}
\end{figure}

\begin{figure}[H]
  \centering
  \fbox{\includegraphics[page=87,width=0.8\textwidth,trim={3cm 4cm 3.75cm 3cm},clip]{\mrsarchive/docs/ORNL-3708.pdf}}
  \caption{complete control rod thimble assembly \parencite[figure 44]{ornl-3708}.}
  % \label{3708-fig40}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=122,width=0.8\textwidth,trim={4cm 4.5cm 4cm 3cm},clip]{\mrsarchive/docs/ORNL-TM-3039.pdf}}
  \caption{reactor access nozzle showing 10- and 2-1/2 in. annuli  \parencite[figure 5.10]{ornl-tm-3229}.}
  \label{3039-fig5-10}
\end{figure}

\subsubsection{outlet strainer}
\textcite[page 24-26]{ornl-tm-3229} states about the outlet strainer:
\enquote{\textit{after the model was built, a strainer structure ... was added to the reactor outlet design which penetrated down into the upper plenum. its purpose was to catch graphite chips (graphite floats in fuel salt) should they break loose from the moderator. this device was not installed in the model but it would not be expected to incluence the flow significantly}}. \\

\parencite[page 84-85]{ornl-tm-0728} states about the outlet stainer:
\enquote{\textit{a strainer made from 16-gage inor-8 plate, with a staggered pattern of 3/32-in.-diam holes on 9/64-in. centers, is built into the top head and access plug assembly to prevent large chips of graphite from circulating with the fuel salt}}.

\begin{figure}[H]
  \centering
  \centering
  \fbox{\includegraphics[page=123,width=0.8\textwidth,trim={4cm 8cm 2.5cm 3.5cm},clip]{\mrsarchive/docs/ORNL-TM-3039.pdf}}
  \caption{reactor fuel outlet strainer \parencite[figure 5.11]{ornl-tm-3229}.}
  \label{3039-fig5-11}
\end{figure}

\textcite[page 115]{ornl-tm-3039} states about the outlet strainer:
\enquote{\textit{stainers were provided at the reactor outlet to prevent passage of graphite chips larger then 1/16 in. a strainer basket was attached to the lower end of the 10-in. nozzle plug and extended downward into the upper head region of the reactor vessel. the three control rod timbles and the graphite sample assembly passed through the stainer basket. since the five graphite elements were not pinned as were the remaining moderator elements, a cross-shaped extension of the basket essembly projected beneath the basket to provide a hold-down}}. this is depicted in figure \ref{3039-fig5-11}. \\

@@

\section{graphite can}
the msre used a graphite moderator consisting of an assembly of graphite stringer with control rods and removable samples rods in the center. bellow is seen the assembly of the can without the removable rods at the center.
\begin{figure}[H]
  \centering
  \fbox{
    \includegraphics[width=0.4\textwidth]{\mrsarchive/img/core-half.jpg}
    \includegraphics[width=0.393\textwidth]{\mrsarchive/img/core-full.jpg}
  }
  \caption{msre graphite core assembly \parencite{ornl}.}
  \label{core-assembly}
\end{figure}
\textcite[page 112 and 114]{ornl-tm-3039} states about the graphite stringers: \enquote{\textit{the reactor core consisted of 617 full and factional sized graphite elements 2x2 in. cross section and about 67 in. long}}. \enquote{\textit{when not buoyed by being immersed in salt, the vertical graphite elements were supported by a lattice of graphite blocks which in turn are supported by a hastelloy-n grid fastened to the bottom of the core can. the core can was thus free to expand downward relative to its top attachment to the reactor vessel while the graphite was free to expand upward relative to its support at the lower end of the core can. the graphite moderator elements were restrained from floating out of core by hastelloy-n rod through holes in the dowel section at the bottom of each graphite element. in addition a wire passing through the upper graphite elements prevented the upper partion of a broken element from floating out of the core}}.
